---
title: "Well Depth and Rainfall Scatter Plot"
format: 
  dashboard: 
    logo: "logo/brenlogo.png"
    orientation: rows
---

# Dangermond

```{r,E3data}
##1 day log
#Loading packages
library(dplyr)
library(dataRetrieval)
library(ggplot2)
library(lubridate)
library(plotly)
# Water depth
#Uploading rain data


#Uploading rain data
E3R<-read.csv("data/rain/Dangermond- Escondido 3 Rain Gauge 20240131-20250401.csv")
E3R$Date<-as.POSIXct(E3R$Date, format="%Y-%m-%d")
E3R<-E3R %>% arrange(E3R$Date)
E3R$Location<-"Escondido 3"

#Uploading well data
E3W<-read.csv("data/Well/Dangermond- Escondido 3 Well 20240101-20250214.csv")
E3W$Date.and.Time<-as.POSIXct(E3W$Date.and.Time,format="%Y-%m-%d %H:%M:%S")
E3W$Date<-format(E3W$Date.and.Time,format="%Y-%m-%d")
E3W$Date<-as.POSIXct(E3W$Date,format="%Y-%m-%d")
E3W<-E3W[E3W$ft..below.ground.<70,]
```

```{r,E3Scatter}
#Preparing to make scatter plot of change in well depth~total storm rainfall
# Create storm number for days with more than 0.1 in of rain
E3_rain_data <- E3R %>%
  mutate(
    rainy = Rain..in. > 0.15,
    gap = !rainy,  # identifies dry days
    storm_group = cumsum(lag(gap, default = TRUE) & rainy)  # increment on first rainy day after dry
  ) %>%
  mutate(
    storm_number = ifelse(rainy, storm_group, NA)  # only assign storm number to rainy days
  )

E3_rain_data <- E3_rain_data %>%
  filter(!is.na(storm_number))


extra_days <- E3_rain_data %>%
  group_by(storm_number) %>%
  slice_tail(n = 1) %>%
  mutate(
    Date = Date + days(1),
    Rain..in. = 0
  )

# Combine original and new rows
df_extended <- bind_rows(E3_rain_data, extra_days) %>%
  arrange(storm_number, Date)

#merge rain data and well data
E3all<-merge(E3W,df_extended,by="Date",all.x=FALSE,all.y=TRUE)

# Step 1: Extract unique rainfall per day per storm
E3_daily_rainfall <- E3all %>%
  select(Date, storm_number, Rain..in.) %>%
  distinct() %>%
  filter(!is.na(storm_number))

E3_daily_rainfall$wtr_yr<-calcWaterYear(E3_daily_rainfall$Date) #Calc water year

# Step 2: Sum rainfall per storm using cleaned daily data
E3_storm_rainfall_summary <- E3_daily_rainfall %>%
  group_by(storm_number,wtr_yr) %>%
  summarise(
    total_rainfall = sum(Rain..in., na.rm = TRUE),
    .groups = "drop"
  )

# Step 3: Get well depth stats (from full merged data)
E3_well_depth_summary <- E3all %>%
  filter(!is.na(storm_number)) %>%
  group_by(storm_number) %>%
  summarise(
    min_well_depth = min(ft..below.ground., na.rm = TRUE),
    max_well_depth = max(ft..below.ground., na.rm = TRUE),
    max_intensity=max(Rain..in.,na.rm=TRUE),
    .groups = "drop"
  )

# Step 4: Join rainfall and well depth summaries
E3_storm_summary <- left_join(E3_well_depth_summary, E3_storm_rainfall_summary, by = "storm_number")
#Calculate difference in well depth
E3_storm_summary$well_change<-E3_storm_summary$max_well_depth-E3_storm_summary$min_well_depth
#change to df so I can read it all
E3_storm_summary<-as.data.frame(E3_storm_summary)

#Take water year into account when calculating storm number
E3_data_with_storm_year <- E3_storm_summary %>%
  filter(!is.na(storm_number)) %>%
  group_by(wtr_yr, storm_number) %>%  # make sure storm_number isn't repeated per storm
  summarise(.groups = "drop_last") %>%     # drop after storm_number to keep water_year grouping
  arrange(wtr_yr, storm_number) %>%
  mutate(storm_in_year = row_number()) %>%
  ungroup()

# Now join back to original data
E3_final_data <- E3_storm_summary %>%
  left_join(E3_data_with_storm_year %>% select(wtr_yr, storm_number,storm_in_year),
            by = c("wtr_yr", "storm_number"))

E3_final_data$Site<-"Escondido 3" #add site neame so i can merge with others later on.

r<-ggplot(E3_final_data)+geom_point(aes(x=total_rainfall,y=well_change,color = max_intensity, size=-storm_in_year))+
  scale_color_gradient(low = "lightyellow", high = "red3", name = "max storm intensity (in/day)")+theme_bw()+
  ggtitle("Rainfall Intensity and Well Water Recharge")
```

```{r, E5data}
E5R<-read.csv("data/rain/Escondido 5 Rain Gauge Rain Gauge 20231001-20250417.csv")
E5R$Date<-as.POSIXct(E5R$Date, format="%Y-%m-%d")
E5R<-E5R %>% arrange(E5R$Date)
E5R$Location<-"Escondido 5"
#Uploading rain data from new device
E5RN<-read.csv("data/rain/Dangermond- Escondido 5 new Rain Gauge 20231001-20250417.csv")
E5RN$Date<-as.POSIXct(E5RN$Date, format="%Y-%m-%d")
E5RN<-E5RN %>% arrange(E5RN$Date)
E5RN$Location<-"Escondido 5"
E5R<-merge(E5R,E5RN,all.x=TRUE,all.y=TRUE) #Merge the 2 rain datasets together

#Uploading well data
E5W<-read.csv("data/Well/Dangermond- Escondido 5 Well 20231001-20250417.csv")
E5W$Date.and.Time<-as.POSIXct(E5W$Date.and.Time,format="%Y-%m-%d %H:%M:%S")
E5W$Date<-format(E5W$Date.and.Time,format="%Y-%m-%d")
E5W$Date<-as.POSIXct(E5W$Date,format="%Y-%m-%d")

#Adjusting escondido 5 well depth data for differential
E5W <- E5W %>%
  mutate(ft..below.ground. = ifelse(ft..below.ground. < 20, ft..below.ground. + 56, ft..below.ground.))
E5W<-E5W[E5W$ft..below.ground.>=53&E5W$ft..below.ground.<=70,]

##Making plot of rainfall quantity and groundwater depth increase
E5<-merge(E5R,E5W,by="Date",all.x=TRUE,all.y=TRUE)
E5Whr<-E5W
```

```{r, E5scatter}

#Preparing to make scatter plot of change in well depth~total storm rainfall
# Create storm number for days with more than 0.1 in of rain
E5_rain_data <- E5R %>%
  mutate(
    rainy = Rain..in. > 0.15,
    gap = !rainy,  # identifies dry days
    storm_group = cumsum(lag(gap, default = TRUE) & rainy)  # increment on first rainy day after dry
  ) %>%
  mutate(
    storm_number = ifelse(rainy, storm_group, NA)  # only assign storm number to rainy days
  )

E5_rain_data <- E5_rain_data %>%
  filter(!is.na(storm_number))

extra_days <- E5_rain_data %>%
  group_by(storm_number) %>%
  slice_tail(n = 1) %>%
  mutate(
    Date = Date + days(1),
    Rain..in. = 0
  )

# Combine original and new rows
df_extended <- bind_rows(E5_rain_data, extra_days) %>%
  arrange(storm_number, Date)

#merge rain data and well data
E5all<-merge(E5Whr,E5_rain_data,by="Date",all.x=FALSE,all.y=TRUE)

# Step 1: Extract unique rainfall per day per storm
daily_rainfall <- E5all %>%
  select(Date, storm_number, Rain..in.) %>%
  distinct() %>%
  filter(!is.na(storm_number))

daily_rainfall$wtr_yr<-calcWaterYear(daily_rainfall$Date) #Calc water year

# Step 2: Sum rainfall per storm using cleaned daily data
storm_rainfall_summary <- daily_rainfall %>%
  group_by(storm_number,wtr_yr) %>%
  summarise(
    total_rainfall = sum(Rain..in., na.rm = TRUE),
    .groups = "drop"
  )

# Step 3: Get well depth stats (from full merged data)
well_depth_summary <- E5all %>%
  filter(!is.na(storm_number)) %>%
  group_by(storm_number) %>%
  summarise(
    min_well_depth = min(ft..below.ground., na.rm = TRUE),
    max_well_depth = max(ft..below.ground., na.rm = TRUE),
    max_intensity=max(Rain..in.,na.rm=TRUE),
    .groups = "drop"
  )

# Step 4: Join rainfall and well depth summaries
storm_summary <- left_join(well_depth_summary, storm_rainfall_summary, by = "storm_number")
#Calculate difference in well depth
storm_summary$well_change<-storm_summary$max_well_depth-storm_summary$min_well_depth
#change to df so I can read it all
storm_summary<-as.data.frame(storm_summary)


#Take water year into account when calculating storm number
data_with_storm_year <- storm_summary %>%
  filter(!is.na(storm_number)) %>%
  group_by(wtr_yr, storm_number) %>%  # make sure storm_number isn't repeated per storm
  summarise(.groups = "drop_last") %>%     # drop after storm_number to keep water_year grouping
  arrange(wtr_yr, storm_number) %>%
  mutate(storm_in_year = row_number()) %>%
  ungroup()

# Now join back to original data
E5_final_data <- storm_summary %>%
  left_join(data_with_storm_year %>% select(wtr_yr, storm_number, storm_in_year),
            by = c("wtr_yr", "storm_number"))

E5_final_data$Site<-"Escondido 5" #add site neame so i can merge with others later on.

r<-ggplot(E5_final_data)+geom_point(aes(x=total_rainfall,y=well_change,color = max_intensity, size=-storm_in_year))+
  scale_color_gradient(low = "lightyellow", high = "red3", name = "max storm intensity (in/day)")+theme_bw()+
  ggtitle("Rainfall Intensity and Well Water Recharge")
```

```{r, E2addin}
#Uploading rain data
E2R<-read.csv("data/rain/Dangermond- Escondido 2 Rain Gauge 20231101-20250408.csv")
E2R$Date<-as.POSIXct(E2R$Date, format="%Y-%m-%d")
E2R<-E2R %>% arrange(E2R$Date)
E2R$Location<-"Escondido 2"

#Uploading well data
E2W<-read.csv("data/Well/Dangermond- Escondido 2 Well 20240101-20250214.csv")
E2W$Date.and.Time<-as.POSIXct(E2W$Date.and.Time,format="%Y-%m-%d %H:%M:%S")
E2W$Date<-format(E2W$Date.and.Time,format="%Y-%m-%d")
E2W$Date<-as.POSIXct(E2W$Date,format="%Y-%m-%d")
E2Whr<-E2W


#Preparing to make scatter plot of change in well depth~total storm rainfall
# Create storm number for days with more than 0.1 in of rain
E2_rain_data <- E2R %>%
  mutate(
    rainy = Rain..in. > 0.15,
    gap = !rainy,  # identifies dry days
    storm_group = cumsum(lag(gap, default = TRUE) & rainy)  # increment on first rainy day after dry
  ) %>%
  mutate(
    storm_number = ifelse(rainy, storm_group, NA)  # only assign storm number to rainy days
  )

E2_rain_data <- E2_rain_data %>%
  filter(!is.na(storm_number))

extra_days <- E2_rain_data %>%
  group_by(storm_number) %>%
  slice_tail(n = 1) %>%
  mutate(
    Date = Date + days(1),
    Rain..in. = 0
  )

# Combine original and new rows
df_extended <- bind_rows(E2_rain_data, extra_days) %>%
  arrange(storm_number, Date)

#merge rain data and well data
E2all<-merge(E2Whr,E2_rain_data,by="Date",all.x=FALSE,all.y=TRUE)

# Step 1: Extract unique rainfall per day per storm
E2_daily_rainfall <- E2all %>%
  select(Date, storm_number, Rain..in.) %>%
  distinct() %>%
  filter(!is.na(storm_number))

E2_daily_rainfall$wtr_yr<-calcWaterYear(E2_daily_rainfall$Date) #Calc water year

# Step 2: Sum rainfall per storm using cleaned daily data
E2_storm_rainfall_summary <- E2_daily_rainfall %>%
  group_by(storm_number,wtr_yr) %>%
  summarise(
    total_rainfall = sum(Rain..in., na.rm = TRUE),
    .groups = "drop"
  )
```

```{r, E2scatter}
# Step 3: Get well depth stats (from full merged data)
E2_well_depth_summary <- E2all %>%
  filter(!is.na(storm_number)) %>%
  group_by(storm_number) %>%
  summarise(
    min_well_depth = min(ft..below.ground., na.rm = TRUE),
    max_well_depth = max(ft..below.ground., na.rm = TRUE),
    max_intensity=max(Rain..in.,na.rm=TRUE),
    .groups = "drop"
  )

# Step 4: Join rainfall and well depth summaries
E2_storm_summary <- left_join(E2_well_depth_summary, E2_storm_rainfall_summary, by = "storm_number")
#Calculate difference in well depth
E2_storm_summary$well_change<-E2_storm_summary$max_well_depth-E2_storm_summary$min_well_depth
#change to df so I can read it all
E2_storm_summary<-as.data.frame(E2_storm_summary)

#Take water year into account when calculating storm number
E2_data_with_storm_year <- E2_storm_summary %>%
  filter(!is.na(storm_number)) %>%
  group_by(wtr_yr, storm_number) %>%  # make sure storm_number isn't repeated per storm
  summarise(.groups = "drop_last") %>%     # drop after storm_number to keep water_year grouping
  arrange(wtr_yr, storm_number) %>%
  mutate(storm_in_year = row_number()) %>%
  ungroup()

# Now join back to original data
E2_final_data <- E2_storm_summary %>%
  left_join(data_with_storm_year %>% select(wtr_yr, storm_number, storm_in_year),
            by = c("wtr_yr", "storm_number"))

E2_final_data$Site<-"Escondido 2" #add site neame so i can merge with others later on.
```

```{r, O5addin}
#Uploading rain data
O5R<-read.csv("data/rain/Dangermond- Oaks 5 Rain Gauge 20240131-20250401.csv")
O5R$Date<-as.POSIXct(O5R$Date, format="%Y-%m-%d")
O5R<-O5R %>% arrange(O5R$Date)
O5R$Location<-"Oaks 5"

#Uploading well data
O5W<-read.csv("data/Well/Dangermond- Oaks 5 Well 20240101-20250214.csv")
O5W$Date.and.Time<-as.POSIXct(O5W$Date.and.Time,format="%Y-%m-%d %H:%M:%S")
O5W$Date<-format(O5W$Date.and.Time,format="%Y-%m-%d")
O5W$Date<-as.POSIXct(O5W$Date,format="%Y-%m-%d")
O5Whr<-O5W


#Preparing to make scatter plot of change in well depth~total storm rainfall
# Create storm number for days with more than 0.1 in of rain
O5_rain_data <- O5R %>%
  mutate(
    rainy = Rain..in. > 0.15,
    gap = !rainy,  # identifies dry days
    storm_group = cumsum(lag(gap, default = TRUE) & rainy)  # increment on first rainy day after dry
  ) %>%
  mutate(
    storm_number = ifelse(rainy, storm_group, NA)  # only assign storm number to rainy days
  )

O5_rain_data <- O5_rain_data %>%
  filter(!is.na(storm_number))

extra_days <- O5_rain_data %>%
  group_by(storm_number) %>%
  slice_tail(n = 1) %>%
  mutate(
    Date = Date + days(1),
    Rain..in. = 0
  )

# Combine original and new rows
df_extended <- bind_rows(O5_rain_data, extra_days) %>%
  arrange(storm_number, Date)

#merge rain data and well data
O5all<-merge(O5Whr,O5_rain_data,by="Date",all.x=FALSE,all.y=TRUE)

# Step 1: Extract unique rainfall per day per storm
O5_daily_rainfall <- O5all %>%
  select(Date, storm_number, Rain..in.) %>%
  distinct() %>%
  filter(!is.na(storm_number))

O5_daily_rainfall$wtr_yr<-calcWaterYear(O5_daily_rainfall$Date) #Calc water year

# Step 2: Sum rainfall per storm using cleaned daily data
O5_storm_rainfall_summary <- O5_daily_rainfall %>%
  group_by(storm_number,wtr_yr) %>%
  summarise(
    total_rainfall = sum(Rain..in., na.rm = TRUE),
    .groups = "drop"
  )
```

```{r, O5scatter}
# Step 3: Get well depth stats (from full merged data)
O5_well_depth_summary <- O5all %>%
  filter(!is.na(storm_number)) %>%
  group_by(storm_number) %>%
  summarise(
    min_well_depth = min(ft..below.ground., na.rm = TRUE),
    max_well_depth = max(ft..below.ground., na.rm = TRUE),
    max_intensity=max(Rain..in.,na.rm=TRUE),
    .groups = "drop"
  )

# Step 4: Join rainfall and well depth summaries
O5_storm_summary <- left_join(O5_well_depth_summary, O5_storm_rainfall_summary, by = "storm_number")
#Calculate difference in well depth
O5_storm_summary$well_change<-O5_storm_summary$max_well_depth-O5_storm_summary$min_well_depth
#change to df so I can read it all
O5_storm_summary<-as.data.frame(O5_storm_summary)

#Take water year into account when calculating storm number
O5_data_with_storm_year <- O5_storm_summary %>%
  filter(!is.na(storm_number)) %>%
  group_by(wtr_yr, storm_number) %>%  # make sure storm_number isn't repeated per storm
  summarise(.groups = "drop_last") %>%     # drop after storm_number to keep water_year grouping
  arrange(wtr_yr, storm_number) %>%
  mutate(storm_in_year = row_number()) %>%
  ungroup()

# Now join back to original data
O5_final_data <- O5_storm_summary %>%
  left_join(data_with_storm_year %>% select(wtr_yr, storm_number, storm_in_year),
            by = c("wtr_yr", "storm_number"))

O5_final_data$Site<-"Oaks 5" #add site neame so i can merge with others later on.

r<-ggplot(O5_final_data)+geom_point(aes(x=total_rainfall,y=well_change,color = max_intensity, size=-storm_in_year))+
  scale_color_gradient(low = "lightyellow", high = "red3", name = "max storm intensity (in/day)")+theme_bw()+
  ggtitle("Rainfall Intensity and Well Water Recharge")
```

```{r, T3addin}
#Uploading rain data
T3R<-read.csv("data/rain/Dangermond- Tinta 3  Rain Gauge 20241001-20250214.csv")
T3R$Date<-as.POSIXct(T3R$Date, format="%Y-%m-%d")
T3R<-T3R %>% arrange(T3R$Date)
T3R$Location<-"Tinta 3"

#Uploading well data
T3W<-read.csv("data/Well/Dangermond- Tinta 3 Well 20241030-20250401.csv")
T3W$Date.and.Time<-as.POSIXct(T3W$Date.and.Time,format="%Y-%m-%d %H:%M:%S")
T3W$Date<-format(T3W$Date.and.Time,format="%Y-%m-%d")
T3W$Date<-as.POSIXct(T3W$Date,format="%Y-%m-%d")
T3Whr<-T3W


#Preparing to make scatter plot of change in well depth~total storm rainfall
# Create storm number for days with more than 0.1 in of rain
T3_rain_data <- T3R %>%
  mutate(
    rainy = Rain..in. > 0.15,
    gap = !rainy,  # identifies dry days
    storm_group = cumsum(lag(gap, default = TRUE) & rainy)  # increment on first rainy day after dry
  ) %>%
  mutate(
    storm_number = ifelse(rainy, storm_group, NA)  # only assign storm number to rainy days
  )

T3_rain_data <- T3_rain_data %>%
  filter(!is.na(storm_number))

extra_days <- T3_rain_data %>%
  group_by(storm_number) %>%
  slice_tail(n = 1) %>%
  mutate(
    Date = Date + days(1),
    Rain..in. = 0
  )

df_extended <- bind_rows(T3_rain_data, extra_days) %>%
  arrange(storm_number, Date)# Combine original and new rows

T3all<-merge(T3Whr,T3_rain_data,by="Date",all.x=FALSE,all.y=TRUE) #merge rain data and well data

T3_daily_rainfall <- T3all %>%
  select(Date, storm_number, Rain..in.) %>%
  distinct() %>%
  filter(!is.na(storm_number))#Extract unique rainfall per day per storm

T3_daily_rainfall$wtr_yr<-calcWaterYear(T3_daily_rainfall$Date) #Calc water year

# Step 2: Sum rainfall per storm using cleaned daily data
T3_storm_rainfall_summary <- T3_daily_rainfall %>%
  group_by(storm_number,wtr_yr) %>%
  summarise(
    total_rainfall = sum(Rain..in., na.rm = TRUE),
    .groups = "drop"
  )
```

```{r, T3scatter}
# Step 3: Get well depth stats (from full merged data)
T3_well_depth_summary <- T3all %>%
  filter(!is.na(storm_number)) %>%
  group_by(storm_number) %>%
  summarise(
    min_well_depth = min(ft..below.ground., na.rm = TRUE),
    max_well_depth = max(ft..below.ground., na.rm = TRUE),
    max_intensity=max(Rain..in.,na.rm=TRUE),
    .groups = "drop"
  )

# Step 4: Join rainfall and well depth summaries
T3_storm_summary <- left_join(T3_well_depth_summary, T3_storm_rainfall_summary, by = "storm_number")
#Calculate difference in well depth
T3_storm_summary$well_change<-T3_storm_summary$max_well_depth-T3_storm_summary$min_well_depth
#change to df so I can read it all
T3_storm_summary<-as.data.frame(T3_storm_summary)

#Take water year into account when calculating storm number
T3_data_with_storm_year <- T3_storm_summary %>%
  filter(!is.na(storm_number)) %>%
  group_by(wtr_yr, storm_number) %>%  # make sure storm_number isn't repeated per storm
  summarise(.groups = "drop_last") %>%     # drop after storm_number to keep water_year grouping
  arrange(wtr_yr, storm_number) %>%
  mutate(storm_in_year = row_number()) %>%
  ungroup()

# Now join back to original data
T3_final_data <- T3_storm_summary %>%
  left_join(T3_data_with_storm_year %>% select(wtr_yr, storm_number, storm_in_year),
            by = c("wtr_yr", "storm_number"))

T3_final_data$Site<-"Tinta 3" #add site neame so i can merge with others later on.

r<-ggplot(T3_final_data)+geom_point(aes(x=total_rainfall,y=well_change,color = storm_in_year),size=3)+
  scale_color_gradient(low = "lightyellow", high = "red3", name = "Storm # in Year")+theme_bw()+
  ggtitle("Rainfall Intensity and Well Water Recharge")
```

```{r,merged}
all_final_data<-rbind(E5_final_data,E3_final_data)
all_final_data<-rbind(all_final_data,E2_final_data)
all_final_data<-rbind(all_final_data,O5_final_data)
all_final_data<-rbind(all_final_data,T3_final_data)

a<-ggplot(all_final_data)+
  geom_point(aes(x=total_rainfall,y=well_change,color = max_intensity, size=-storm_in_year,
                 text = paste0("<br>Total Rain (in): ", total_rainfall, " in",
                    "<br>Storm Number: ", storm_number,
                    "<br>Site: ", Site,"<br>Max Intensity: ", max_intensity, " in/day",
                    "<br>Well Change: ", well_change, " feet")))+
  scale_color_gradient(low = "lightyellow", high = "red3", name = "Max Storm intensity (in/hr)") +
  scale_size_continuous(name = "Storm number in Year")+theme_bw()+
  ggtitle("Rainfall Intensity and Well Water Rise")


ggplotly(a,tooltip = "text")
```

In this plot a storm is considered consecutive days of more than 0.15 inches of rain. The intensity, visualized by the color is the maximum daily rainfall for the duration of the storm. the value of 0.15 as the storm cutoff is somewhat arbetrary and may be changed for future analysis. For puposes here, 0.15 is the value in which we start seeing an affect on groundwater level, but this could be different for different wells. The storm number is the number storm it is in the year of the given site selection. If a site device is installed halfway through the rainy season and there is no way to tell how many storms happened prior to installation the first storm after installation is considered storm 1. All sites for this figure are from the jack and Laura Dangermond preserve.


```{r, Coopaddin}
#Uploading rain data
CoopR<-read.csv("data/rain/Las Piletas Cooper Rain Gauge 20241205-20250214.csv")
CoopR$Date<-as.POSIXct(CoopR$Date, format="%Y-%m-%d")
CoopR<-CoopR %>% arrange(CoopR$Date)
CoopR$Location<-"Cooper"

#Uploading well data
CoopW<-read.csv("data/Las Piletas Cooper Well 20241211-20250505.csv")
CoopW$Date.and.Time<-as.POSIXct(CoopW$Date.and.Time,format="%Y-%m-%d %H:%M:%S")
CoopW$Date<-format(CoopW$Date.and.Time,format="%Y-%m-%d")
CoopW$Date<-as.POSIXct(CoopW$Date,format="%Y-%m-%d")
CoopWhr<-CoopW


#Preparing to make scatter plot of change in well depth~total storm rainfall
# Create storm number for days with more than 0.1 in of rain
Coop_rain_data <- CoopR %>%
  mutate(
    rainy = Rain..in. > 0.15,
    gap = !rainy,  # identifies dry days
    storm_group = cumsum(lag(gap, default = TRUE) & rainy)  # increment on first rainy day after dry
  ) %>%
  mutate(
    storm_number = ifelse(rainy, storm_group, NA)  # only assign storm number to rainy days
  )

Coop_rain_data <- Coop_rain_data %>%
  filter(!is.na(storm_number))

extra_days <- Coop_rain_data %>%
  group_by(storm_number) %>%
  slice_tail(n = 1) %>%
  mutate(
    Date = Date + days(1),
    Rain..in. = 0
  )

df_extended <- bind_rows(Coop_rain_data, extra_days) %>%
  arrange(storm_number, Date)# Combine original and new rows

Coopall<-merge(CoopWhr,Coop_rain_data,by="Date",all.x=FALSE,all.y=TRUE) #merge rain data and well data

Coop_daily_rainfall <- Coopall %>%
  select(Date, storm_number, Rain..in.) %>%
  distinct() %>%
  filter(!is.na(storm_number))#Extract unique rainfall per day per storm

Coop_daily_rainfall$wtr_yr<-calcWaterYear(Coop_daily_rainfall$Date) #Calc water year

# Step 2: Sum rainfall per storm using cleaned daily data
Coop_storm_rainfall_summary <- Coop_daily_rainfall %>%
  group_by(storm_number,wtr_yr) %>%
  summarise(
    total_rainfall = sum(Rain..in., na.rm = TRUE),
    .groups = "drop"
  )
```

```{r, Coopscatter}
# Step 3: Get well depth stats (from full merged data)
Coop_well_depth_summary <- Coopall %>%
  filter(!is.na(storm_number)) %>%
  group_by(storm_number) %>%
  summarise(
    min_well_depth = min(ft..below.ground., na.rm = TRUE),
    max_well_depth = max(ft..below.ground., na.rm = TRUE),
    max_intensity=max(Rain..in.,na.rm=TRUE),
    .groups = "drop"
  )

# Step 4: Join rainfall and well depth summaries
Coop_storm_summary <- left_join(Coop_well_depth_summary, Coop_storm_rainfall_summary, by = "storm_number")
#Calculate difference in well depth
Coop_storm_summary$well_change<-Coop_storm_summary$max_well_depth-Coop_storm_summary$min_well_depth
#change to df so I can read it all
Coop_storm_summary<-as.data.frame(Coop_storm_summary)

#Take water year into account when calculating storm number
Coop_data_with_storm_year <- Coop_storm_summary %>%
  filter(!is.na(storm_number)) %>%
  group_by(wtr_yr, storm_number) %>%  # make sure storm_number isn't repeated per storm
  summarise(.groups = "drop_last") %>%     # drop after storm_number to keep water_year grouping
  arrange(wtr_yr, storm_number) %>%
  mutate(storm_in_year = row_number()) %>%
  ungroup()

# Now join back to original data
Coop_final_data <- Coop_storm_summary %>%
  left_join(Coop_data_with_storm_year %>% select(wtr_yr, storm_number, storm_in_year),
            by = c("wtr_yr", "storm_number"))

Coop_final_data$Site<-"Cooper" #add site neame so i can merge with others later on.

r<-ggplot(Coop_final_data)+geom_point(aes(x=total_rainfall,y=well_change,color = storm_in_year),size=3)+
  scale_color_gradient(low = "lightyellow", high = "red3", name = "Storm # in Year")+theme_bw()+
  ggtitle("Rainfall Intensity and Well Water Recharge")
```

```{r, NEaddin}
#Uploading rain data
NER<-read.csv("data/rain/Las Piletas NE Corner Rain Gauge Rain Gauge 20241211-20250530.csv")
NER$Date<-as.POSIXct(NER$Date, format="%Y-%m-%d")
NER<-NER %>% arrange(NER$Date)
NER$Location<-"NE Corner"

#Uploading well data
NEW<-read.csv("data/Well/Las Piletas NE Corner Well 20241211-20250530.csv")
NEW$Date.and.Time<-as.POSIXct(NEW$Date.and.Time,format="%Y-%m-%d %H:%M:%S")
NEW$Date<-format(NEW$Date.and.Time,format="%Y-%m-%d")
NEW$Date<-as.POSIXct(NEW$Date,format="%Y-%m-%d")
NEWhr<-NEW


#Preparing to make scatter plot of change in well depth~total storm rainfall
# Create storm number for days with more than 0.1 in of rain
NE_rain_data <- NER %>%
  mutate(
    rainy = Rain..in. > 0.15,
    gap = !rainy,  # identifies dry days
    storm_group = cumsum(lag(gap, default = TRUE) & rainy)  # increment on first rainy day after dry
  ) %>%
  mutate(
    storm_number = ifelse(rainy, storm_group, NA)  # only assign storm number to rainy days
  )

NE_rain_data <- NE_rain_data %>%
  filter(!is.na(storm_number))

extra_days <- NE_rain_data %>%
  group_by(storm_number) %>%
  slice_tail(n = 1) %>%
  mutate(
    Date = Date + days(1),
    Rain..in. = 0
  )

df_extended <- bind_rows(NE_rain_data, extra_days) %>%
  arrange(storm_number, Date)# Combine original and new rows

NEall<-merge(NEWhr,NE_rain_data,by="Date",all.x=FALSE,all.y=TRUE) #merge rain data and well data

NE_daily_rainfall <- NEall %>%
  select(Date, storm_number, Rain..in.) %>%
  distinct() %>%
  filter(!is.na(storm_number))#Extract unique rainfall per day per storm

NE_daily_rainfall$wtr_yr<-calcWaterYear(NE_daily_rainfall$Date) #Calc water year

# Step 2: Sum rainfall per storm using cleaned daily data
NE_storm_rainfall_summary <- NE_daily_rainfall %>%
  group_by(storm_number,wtr_yr) %>%
  summarise(
    total_rainfall = sum(Rain..in., na.rm = TRUE),
    .groups = "drop"
  )
```

```{r, NEscatter}
# Step 3: Get well depth stats (from full merged data)
NE_well_depth_summary <- NEall %>%
  filter(!is.na(storm_number)) %>%
  group_by(storm_number) %>%
  summarise(
    min_well_depth = min(ft..below.ground., na.rm = TRUE),
    max_well_depth = max(ft..below.ground., na.rm = TRUE),
    max_intensity=max(Rain..in.,na.rm=TRUE),
    .groups = "drop"
  )

# Step 4: Join rainfall and well depth summaries
NE_storm_summary <- left_join(NE_well_depth_summary, NE_storm_rainfall_summary, by = "storm_number")
#Calculate difference in well depth
NE_storm_summary$well_change<-NE_storm_summary$max_well_depth-NE_storm_summary$min_well_depth
#change to df so I can read it all
NE_storm_summary<-as.data.frame(NE_storm_summary)

#Take water year into account when calculating storm number
NE_data_with_storm_year <- NE_storm_summary %>%
  filter(!is.na(storm_number)) %>%
  group_by(wtr_yr, storm_number) %>%  # make sure storm_number isn't repeated per storm
  summarise(.groups = "drop_last") %>%     # drop after storm_number to keep water_year grouping
  arrange(wtr_yr, storm_number) %>%
  mutate(storm_in_year = row_number()) %>%
  ungroup()

# Now join back to original data
NE_final_data <- NE_storm_summary %>%
  left_join(NE_data_with_storm_year %>% select(wtr_yr, storm_number, storm_in_year),
            by = c("wtr_yr", "storm_number"))

NE_final_data$Site<-"NE Corner" #add site neame so i can merge with others later on.

r<-ggplot(NE_final_data)+geom_point(aes(x=total_rainfall,y=well_change,color = storm_in_year),size=3)+
  scale_color_gradient(low = "lightyellow", high = "red3", name = "Storm # in Year")+theme_bw()+
  ggtitle("Rainfall Intensity and Well Water Recharge")
```

```{r, Windaddin}
#Uploading rain data
WindR<-read.csv("data/rain/Las Piletas Windmill Rain Gauge Rain Gauge 20250224-20250530.csv")
WindR$Date<-as.POSIXct(WindR$Date, format="%Y-%m-%d")
WindR<-WindR %>% arrange(WindR$Date)
WindR$Location<-"Windmill"

#Uploading well data
WindW<-read.csv("data/Well/Las Piletas Windmill Well 20250227-20250530.csv")
WindW$Date.and.Time<-as.POSIXct(WindW$Date.and.Time,format="%Y-%m-%d %H:%M:%S")
WindW$Date<-format(WindW$Date.and.Time,format="%Y-%m-%d")
WindW$Date<-as.POSIXct(WindW$Date,format="%Y-%m-%d")
WindWhr<-WindW


#Preparing to make scatter plot of change in well depth~total storm rainfall
# Create storm number for days with more than 0.1 in of rain
Wind_rain_data <- WindR %>%
  mutate(
    rainy = Rain..in. > 0.15,
    gap = !rainy,  # identifies dry days
    storm_group = cumsum(lag(gap, default = TRUE) & rainy)  # increment on first rainy day after dry
  ) %>%
  mutate(
    storm_number = ifelse(rainy, storm_group, NA)  # only assign storm number to rainy days
  )

Wind_rain_data <- Wind_rain_data %>%
  filter(!is.na(storm_number))

extra_days <- Wind_rain_data %>%
  group_by(storm_number) %>%
  slice_tail(n = 1) %>%
  mutate(
    Date = Date + days(1),
    Rain..in. = 0
  )

df_extended <- bind_rows(Wind_rain_data, extra_days) %>%
  arrange(storm_number, Date)# Combine original and new rows

Windall<-merge(WindWhr,Wind_rain_data,by="Date",all.x=FALSE,all.y=TRUE) #merge rain data and well data

Wind_daily_rainfall <- Windall %>%
  select(Date, storm_number, Rain..in.) %>%
  distinct() %>%
  filter(!is.na(storm_number))#Extract unique rainfall per day per storm

Wind_daily_rainfall$wtr_yr<-calcWaterYear(Wind_daily_rainfall$Date) #Calc water year

# Step 2: Sum rainfall per storm using cleaned daily data
Wind_storm_rainfall_summary <- Wind_daily_rainfall %>%
  group_by(storm_number,wtr_yr) %>%
  summarise(
    total_rainfall = sum(Rain..in., na.rm = TRUE),
    .groups = "drop"
  )
```

```{r, Windscatter}
# Step 3: Get well depth stats (from full merged data)
Wind_well_depth_summary <- Windall %>%
  filter(!is.na(storm_number)) %>%
  group_by(storm_number) %>%
  summarise(
    min_well_depth = min(ft..below.ground., na.rm = TRUE),
    max_well_depth = max(ft..below.ground., na.rm = TRUE),
    max_intensity=max(Rain..in.,na.rm=TRUE),
    .groups = "drop"
  )

# Step 4: Join rainfall and well depth summaries
Wind_storm_summary <- left_join(Wind_well_depth_summary, Wind_storm_rainfall_summary, by = "storm_number")
#Calculate difference in well depth
Wind_storm_summary$well_change<-Wind_storm_summary$max_well_depth-Wind_storm_summary$min_well_depth
#change to df so I can read it all
Wind_storm_summary<-as.data.frame(Wind_storm_summary)

#Take water year into account when calculating storm number
Wind_data_with_storm_year <- Wind_storm_summary %>%
  filter(!is.na(storm_number)) %>%
  group_by(wtr_yr, storm_number) %>%  # make sure storm_number isn't repeated per storm
  summarise(.groups = "drop_last") %>%     # drop after storm_number to keep water_year grouping
  arrange(wtr_yr, storm_number) %>%
  mutate(storm_in_year = row_number()) %>%
  ungroup()

# Now join back to original data
Wind_final_data <- Wind_storm_summary %>%
  left_join(Wind_data_with_storm_year %>% select(wtr_yr, storm_number, storm_in_year),
            by = c("wtr_yr", "storm_number"))

Wind_final_data$Site<-"Windmill" #add site neame so i can merge with others later on.

r<-ggplot(Wind_final_data)+geom_point(aes(x=total_rainfall,y=well_change,color = storm_in_year),size=3)+
  scale_color_gradient(low = "lightyellow", high = "red3", name = "Storm # in Year")+theme_bw()+
  ggtitle("Rainfall Intensity and Well Water Recharge")
```

```{r, CPaddin}
#Uploading rain data
CPR<-read.csv("data/rain/Randall cactus pasture rain gauge Rain Gauge 20250301-20250527.csv")
CPR$Date<-as.POSIXct(CPR$Date, format="%Y-%m-%d")
CPR<-CPR %>% arrange(CPR$Date)
CPR$Location<-"Cactus Pasture"

#Uploading well data
CPW<-read.csv("data/Well/Randall cactus pasture Well 20250301-20250530.csv")
CPW$Date.and.Time<-as.POSIXct(CPW$Date.and.Time,format="%Y-%m-%d %H:%M:%S")
CPW$Date<-format(CPW$Date.and.Time,format="%Y-%m-%d")
CPW$Date<-as.POSIXct(CPW$Date,format="%Y-%m-%d")
CPWhr<-CPW


#Preparing to make scatter plot of change in well depth~total storm rainfall
# Create storm number for days with more than 0.1 in of rain
CP_rain_data <- CPR %>%
  mutate(
    rainy = Rain..in. > 0.15,
    gap = !rainy,  # identifies dry days
    storm_group = cumsum(lag(gap, default = TRUE) & rainy)  # increment on first rainy day after dry
  ) %>%
  mutate(
    storm_number = ifelse(rainy, storm_group, NA)  # only assign storm number to rainy days
  )

CP_rain_data <- CP_rain_data %>%
  filter(!is.na(storm_number))

extra_days <- CP_rain_data %>%
  group_by(storm_number) %>%
  slice_tail(n = 1) %>%
  mutate(
    Date = Date + days(1),
    Rain..in. = 0
  )

df_extended <- bind_rows(CP_rain_data, extra_days) %>%
  arrange(storm_number, Date)# Combine original and new rows

CPall<-merge(CPWhr,CP_rain_data,by="Date",all.x=FALSE,all.y=TRUE) #merge rain data and well data

CP_daily_rainfall <- CPall %>%
  select(Date, storm_number, Rain..in.) %>%
  distinct() %>%
  filter(!is.na(storm_number))#Extract unique rainfall per day per storm

CP_daily_rainfall$wtr_yr<-calcWaterYear(CP_daily_rainfall$Date) #Calc water year

# Step 2: Sum rainfall per storm using cleaned daily data
CP_storm_rainfall_summary <- CP_daily_rainfall %>%
  group_by(storm_number,wtr_yr) %>%
  summarise(
    total_rainfall = sum(Rain..in., na.rm = TRUE),
    .groups = "drop"
  )
```

```{r, CPscatter}
# Step 3: Get well depth stats (from full merged data)
CP_well_depth_summary <- CPall %>%
  filter(!is.na(storm_number)) %>%
  group_by(storm_number) %>%
  summarise(
    min_well_depth = min(ft..below.ground., na.rm = TRUE),
    max_well_depth = max(ft..below.ground., na.rm = TRUE),
    max_intensity=max(Rain..in.,na.rm=TRUE),
    .groups = "drop"
  )

# Step 4: Join rainfall and well depth summaries
CP_storm_summary <- left_join(CP_well_depth_summary, CP_storm_rainfall_summary, by = "storm_number")
#Calculate difference in well depth
CP_storm_summary$well_change<-CP_storm_summary$max_well_depth-CP_storm_summary$min_well_depth
#change to df so I can read it all
CP_storm_summary<-as.data.frame(CP_storm_summary)

#Take water year into account when calculating storm number
CP_data_with_storm_year <- CP_storm_summary %>%
  filter(!is.na(storm_number)) %>%
  group_by(wtr_yr, storm_number) %>%  # make sure storm_number isn't repeated per storm
  summarise(.groups = "drop_last") %>%     # drop after storm_number to keep water_year grouping
  arrange(wtr_yr, storm_number) %>%
  mutate(storm_in_year = row_number()) %>%
  ungroup()

# Now join back to original data
CP_final_data <- CP_storm_summary %>%
  left_join(CP_data_with_storm_year %>% select(wtr_yr, storm_number, storm_in_year),
            by = c("wtr_yr", "storm_number"))

CP_final_data$Site<-"Cactus Pasture" #add site neame so i can merge with others later on.

r<-ggplot(CP_final_data)+geom_point(aes(x=total_rainfall,y=well_change,color = storm_in_year),size=3)+
  scale_color_gradient(low = "lightyellow", high = "red3", name = "Storm # in Year")+theme_bw()+
  ggtitle("Rainfall Intensity and Well Water Recharge")
```

```{r, LTaddin}
#Uploading rain data
LTR<-read.csv("data/rain/Randall Lower tweedy rain gauge Rain Gauge 20250301-20250527.csv")
LTR$Date<-as.POSIXct(LTR$Date, format="%Y-%m-%d")
LTR<-LTR %>% arrange(LTR$Date)
LTR$Location<-"Lower Tweedy"

#Uploading well data
LTW<-read.csv("data/Well/Randall Lower Tweedy Well 20250301-20250617.csv")
LTW$Date.and.Time<-as.POSIXct(LTW$Date.and.Time,format="%Y-%m-%d %H:%M:%S")
LTW$Date<-format(LTW$Date.and.Time,format="%Y-%m-%d")
LTW$Date<-as.POSIXct(LTW$Date,format="%Y-%m-%d")
LTWhr<-LTW


#Preparing to make scatter plot of change in well depth~total storm rainfall
# Create storm number for days with more than 0.1 in of rain
LT_rain_data <- LTR %>%
  mutate(
    rainy = Rain..in. > 0.15,
    gap = !rainy,  # identifies dry days
    storm_group = cumsum(lag(gap, default = TRUE) & rainy)  # increment on first rainy day after dry
  ) %>%
  mutate(
    storm_number = ifelse(rainy, storm_group, NA)  # only assign storm number to rainy days
  )

LT_rain_data <- LT_rain_data %>%
  filter(!is.na(storm_number))

extra_days <- LT_rain_data %>%
  group_by(storm_number) %>%
  slice_tail(n = 1) %>%
  mutate(
    Date = Date + days(1),
    Rain..in. = 0
  )

df_extended <- bind_rows(LT_rain_data, extra_days) %>%
  arrange(storm_number, Date)# Combine original and new rows

LTall<-merge(LTWhr,LT_rain_data,by="Date",all.x=FALSE,all.y=TRUE) #merge rain data and well data

LT_daily_rainfall <- LTall %>%
  select(Date, storm_number, Rain..in.) %>%
  distinct() %>%
  filter(!is.na(storm_number))#Extract unique rainfall per day per storm

LT_daily_rainfall$wtr_yr<-calcWaterYear(LT_daily_rainfall$Date) #Calc water year

# Step 2: Sum rainfall per storm using cleaned daily data
LT_storm_rainfall_summary <- LT_daily_rainfall %>%
  group_by(storm_number,wtr_yr) %>%
  summarise(
    total_rainfall = sum(Rain..in., na.rm = TRUE),
    .groups = "drop"
  )
```

```{r, LTscatter}
# Step 3: Get well depth stats (from full merged data)
LT_well_depth_summary <- LTall %>%
  filter(!is.na(storm_number)) %>%
  group_by(storm_number) %>%
  summarise(
    min_well_depth = min(ft..below.ground., na.rm = TRUE),
    max_well_depth = max(ft..below.ground., na.rm = TRUE),
    max_intensity=max(Rain..in.,na.rm=TRUE),
    .groups = "drop"
  )

# Step 4: Join rainfall and well depth summaries
LT_storm_summary <- left_join(LT_well_depth_summary, LT_storm_rainfall_summary, by = "storm_number")
#Calculate difference in well depth
LT_storm_summary$well_change<-LT_storm_summary$max_well_depth-LT_storm_summary$min_well_depth
#change to df so I can read it all
LT_storm_summary<-as.data.frame(LT_storm_summary)

#Take water year into account when calculating storm number
LT_data_with_storm_year <- LT_storm_summary %>%
  filter(!is.na(storm_number)) %>%
  group_by(wtr_yr, storm_number) %>%  # make sure storm_number isn't repeated per storm
  summarise(.groups = "drop_last") %>%     # drop after storm_number to keep water_year grouping
  arrange(wtr_yr, storm_number) %>%
  mutate(storm_in_year = row_number()) %>%
  ungroup()

# Now join back to original data
LT_final_data <- LT_storm_summary %>%
  left_join(LT_data_with_storm_year %>% select(wtr_yr, storm_number, storm_in_year),
            by = c("wtr_yr", "storm_number"))

LT_final_data$Site<-"Lower Tweedy" #add site neame so i can merge with others later on.

r<-ggplot(LT_final_data)+geom_point(aes(x=total_rainfall,y=well_change,color = storm_in_year),size=3)+
  scale_color_gradient(low = "lightyellow", high = "red3", name = "Storm # in Year")+theme_bw()+
  ggtitle("Rainfall Intensity and Well Water Recharge")
```

```{r, BCaddin}
#Uploading rain data
BCR<-read.csv("data/rain/Randall B and C Ranch. Rain gauge Rain Gauge 20250301-20250527.csv")
BCR$Date<-as.POSIXct(BCR$Date, format="%Y-%m-%d")
BCR<-BCR %>% arrange(BCR$Date)
BCR$Location<-"B and C well"

#Uploading well data
BCW<-read.csv("data/Well/Randall B and C ranch well Well 20250301-20250617.csv")
BCW$Date.and.Time<-as.POSIXct(BCW$Date.and.Time,format="%Y-%m-%d %H:%M:%S")
BCW$Date<-format(BCW$Date.and.Time,format="%Y-%m-%d")
BCW$Date<-as.POSIXct(BCW$Date,format="%Y-%m-%d")
BCWhr<-BCW


#Preparing to make scatter plot of change in well depth~total storm rainfall
# Create storm number for days with more than 0.1 in of rain
BC_rain_data <- BCR %>%
  mutate(
    rainy = Rain..in. > 0.15,
    gap = !rainy,  # identifies dry days
    storm_group = cumsum(lag(gap, default = TRUE) & rainy)  # increment on first rainy day after dry
  ) %>%
  mutate(
    storm_number = ifelse(rainy, storm_group, NA)  # only assign storm number to rainy days
  )

BC_rain_data <- BC_rain_data %>%
  filter(!is.na(storm_number))

extra_days <- BC_rain_data %>%
  group_by(storm_number) %>%
  slice_tail(n = 1) %>%
  mutate(
    Date = Date + days(1),
    Rain..in. = 0
  )

df_extended <- bind_rows(BC_rain_data, extra_days) %>%
  arrange(storm_number, Date)# Combine original and new rows

BCall<-merge(BCWhr,BC_rain_data,by="Date",all.x=FALSE,all.y=TRUE) #merge rain data and well data

BC_daily_rainfall <- BCall %>%
  select(Date, storm_number, Rain..in.) %>%
  distinct() %>%
  filter(!is.na(storm_number))#Extract unique rainfall per day per storm

BC_daily_rainfall$wtr_yr<-calcWaterYear(BC_daily_rainfall$Date) #Calc water year

# Step 2: Sum rainfall per storm using cleaned daily data
BC_storm_rainfall_summary <- BC_daily_rainfall %>%
  group_by(storm_number,wtr_yr) %>%
  summarise(
    total_rainfall = sum(Rain..in., na.rm = TRUE),
    .groups = "drop"
  )
```

```{r, BCscatter}
# Step 3: Get well depth stats (from full merged data)
BC_well_depth_summary <- BCall %>%
  filter(!is.na(storm_number)) %>%
  group_by(storm_number) %>%
  summarise(
    min_well_depth = min(ft..below.ground., na.rm = TRUE),
    max_well_depth = max(ft..below.ground., na.rm = TRUE),
    max_intensity=max(Rain..in.,na.rm=TRUE),
    .groups = "drop"
  )

# Step 4: Join rainfall and well depth summaries
BC_storm_summary <- left_join(BC_well_depth_summary, BC_storm_rainfall_summary, by = "storm_number")
#Calculate difference in well depth
BC_storm_summary$well_change<-BC_storm_summary$max_well_depth-BC_storm_summary$min_well_depth
#change to df so I can read it all
BC_storm_summary<-as.data.frame(BC_storm_summary)

#Take water year into account when calculating storm number
BC_data_with_storm_year <- BC_storm_summary %>%
  filter(!is.na(storm_number)) %>%
  group_by(wtr_yr, storm_number) %>%  # make sure storm_number isn't repeated per storm
  summarise(.groups = "drop_last") %>%     # drop after storm_number to keep water_year grouping
  arrange(wtr_yr, storm_number) %>%
  mutate(storm_in_year = row_number()) %>%
  ungroup()

# Now join back to original data
BC_final_data <- BC_storm_summary %>%
  left_join(BC_data_with_storm_year %>% select(wtr_yr, storm_number, storm_in_year),
            by = c("wtr_yr", "storm_number"))

BC_final_data$Site<-"B and C" #add site neame so i can merge with others later on.

r<-ggplot(BC_final_data)+geom_point(aes(x=total_rainfall,y=well_change,color = storm_in_year),size=3)+
  scale_color_gradient(low = "lightyellow", high = "red3", name = "Storm # in Year")+theme_bw()+
  ggtitle("Rainfall Intensity and Well Water Recharge")
```

```{r,mergedLpPandRandall}
all_final_data<-rbind(Wind_final_data,NE_final_data)
all_final_data<-rbind(Coop_final_data,all_final_data)
all_final_data<-rbind(BC_final_data,all_final_data)
all_final_data<-rbind(LT_final_data,all_final_data)
all_final_data<-rbind(CP_final_data,all_final_data)

a<-ggplot(all_final_data)+
  geom_point(aes(x=total_rainfall,y=well_change,color = max_intensity, size=-storm_in_year))+
  scale_color_gradient(low = "lightyellow", high = "red3", name = "Max Storm intensity (in/hr)") +
  scale_size_continuous(name = "Storm number in Year")+theme_bw()+
  ggtitle("Rainfall Intensity and Well Water Rise")


ggplotly(a)
```