---
title: "Las Piletas"
format: 
  dashboard: 
    orientation: rows
---


```{r, loadpackages}
#load packages that are needed for all dashboards
library(tidyverse)
library(plotly)             
#library(reactable)
#library(bslib)
library(dplyr)
#library(leaflet)
#library(bsicons)
#library(shiny)
library(ggplot2)
library(readr)
set.seed(4242)
```
# Las Piletas

On Average 3653 gallons are pumped per day from the Cooper well from April 28-May 9th 2025. That equates to 1.3 million gallons or 4.1 acre feet per year. 

Groundwater receeds by about X inches per day. If this pattern continues water level would decrease by X feet per year and X feet of recharge were observed in the 2025 water year.

With no pumping and just environmental influencers in play the groundwater receeds by x inches per day

```{r,calculateLasPiletasValues}
#Cooper well is used to fill head quarters tank, a 10,000 gallon tank that is 87 inches tall
#=114.9 gallons per inch


#1. load pump data
HQtank<-read.csv("data/HQ Tanks Water Tank 20250310-20250509.csv")
HQtank$Date.and.Time<-as.POSIXct(HQtank$Date.and.Time)

start<-"2025/04/28 05:00:00"
end<-"2025/05/09 05:40:00"

HQtank_osc<-HQtank[HQtank$Date.and.Time>start &HQtank$Date.and.Time<end,]

HQtank_osc<-HQtank_osc %>%
  mutate(Date = as.Date(Date.and.Time))

colnames(HQtank_osc)<-c("DateTime","Level_in","Volume_gal","Date")
```

```{r,TankPlotandStats}
q<-ggplot(data=HQtank_osc,aes(x=DateTime,y=Volume_gal))+geom_line()
ggplotly(q)

#calculate daily max and daily min
HQtank_stats <- HQtank_osc %>%
  group_by(Date) %>%
  summarize(
    DailyMax = max(Volume_gal, na.rm = TRUE),
    DailyMin = min(Volume_gal, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  arrange(Date)

#
HQtank_stats <- HQtank_stats %>%
  mutate(
    Dailydraw = lag(DailyMax)-DailyMin
  ) %>%
  ungroup()


# Remove the first two days per site
HQtank_stats <- HQtank_stats %>%
  slice(-(1)) 

mean_Draw <- mean(HQtank_stats$Dailydraw)
sd_Draw <- sd(HQtank_stats$Dailydraw)
max_Draw <- max(HQtank_stats$Dailydraw)
min_Draw <- min(HQtank_stats$Dailydraw)

#5. calculate draw down of pump at 3653.364 gallon per day resulted in X draw down

#6. 
coop<-read.csv("data/Las Piletas Cooper Well 20250427-20250509.csv")
coop$Date.and.Time<-as.POSIXct(coop$Date.and.Time)
colnames(coop)<-c("DateTime","Depth_to_Water_ft")
#Matching with Joe from slo county manual meaurement
coop$Depth_to_Water_ft<-coop$Depth_to_Water_ft+43.6
pump<-read.csv("data/Cooper_Pump_Control.csv")
pump <- pump %>%
  mutate(OnOff = ifelse(Action == "Turned on by automation due to the destination tank's levels", "on",
                        ifelse(Action == "Turned off by automation due to the destination tank's levels", "off", NA)))
pump$DateTime<-as.POSIXct(pump$DateTime)
Cooper<-merge(coop,pump,by="DateTime",all.x=TRUE,all.y=TRUE)
#Cooper<-merge(Cooper,HQtank_osc,by="DateTime",all.x=TRUE,all.y=TRUE)
```

```{r,WellPlot}

##Just well depth
q<-ggplot(data=coop,aes(x=DateTime))+
  geom_line(aes(y=Depth_to_Water_ft))+scale_y_reverse()+theme_bw()
ggplotly(q)

#End goal when X gallons per day are pumped groundwater receeds by X inches per day. With no pumping and just environmental influencers in play the groundwater receeds by x inches per day

#Pumping intensity could affect the recovery time for back to a normal well depth Ex. Jan 6 pump event resulted in 6 days to recover to normal with a drawdown of 95 feet during pumping, while April 2 only took 1 day with a drawdown of 38 feet during pumping

# Get line length to span y-axis (adjust as needed)
#y_min <- min(Cooper$Depth_to_Water_ft, na.rm = TRUE)
#y_max <- max(Cooper$Depth_to_Water_ft, na.rm = TRUE)

# Create a transition dataset
#vlines_df <- Cooper %>%
#  filter(OnOff %in% c("on", "off")) %>%
#  mutate(
#    color = ifelse(OnOff == "on", "red", "lightblue")
#  )

# Create plot using geom_segment
#q <- ggplot(Cooper, aes(x = DateTime, y = Depth_to_Water_ft)) +
# geom_line() +
#  geom_segment(
#    data = vlines_df,
#    aes(x = DateTime, xend = DateTime, y = y_min, yend = y_max, color = color),
#   linetype = "dashed", alpha = 0.5
#  ) +
#  scale_color_identity() +  # Use actual colors in the color column
#  scale_y_reverse() +
#  theme_bw()
```



```{r}
#Cooper well math
coop$Date<-as.Date(coop$DateTime)
coopdaily_min<-aggregate(Depth_to_Water_ft~Date,coop,FUN=min)


gwallhr<-read.csv("data/hourly_well_data.csv")
gwallhr$Date.and.Time<-as.POSIXct(gwallhr$Date.and.Time,format="%Y-%m-%d %H:%M:%S")

Coopall<-gwallhr[gwallhr$Well_Name=="Cooper",]

q<-ggplot(data=coop,aes(x=DateTime))+
  geom_line(aes(y=Depth_to_Water_ft))+scale_y_reverse()+theme_bw()
ggplotly(q)

r<-ggplot(data=Coopall,aes(x=Date.and.Time))+
  geom_line(aes(y=ft..below.ground.))+scale_y_reverse()+theme_bw()
ggplotly(r)
```


















